### 2022-01-05 paper/paper.tex
Revisions based on the review by John F. Gibson (#21)
* mention number of DOFs

* additional performance reference

* add some missing hyphens

* visualization of IC and mesh for PID runs

* comment on parallelization

* change caption of mesh plot to indicate that it is a slice

* suggestions from Andrew

Co-authored-by: Andrew Winters <andrew.ross.winters@liu.se>

Co-authored-by: Andrew Winters <andrew.ross.winters@liu.se>

Currently, \trixi provides shared-memory parallelization via multithreading.
Distributed-memory parallelization with MPI is available for some mesh types
but still work in progress.

@@

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. This results in $64 (\text{\lstinline{polydeg}}+1)^3$ degrees
of freedom (DG nodes) when polynomials of degree \lstinline{polydeg} are used.
To make the mesh curvilinear, the interior of the box is heavily warped by
a mapping adapted from \cite{chan2019efficient}.
Specifically, we map Cartesian reference coordinates $(\xi, \eta, \zeta)$ to
physical coordinates $(x, y, z)$ via the transformation
\begin{equation}
\begin{aligned}
  y &= \eta  + 0.15 \bigl( \cos(1.5 \pi \xi) \cos(0.5 \pi \eta) \cos(0.5 \pi \zeta) \bigr),
  \\
  x &= \xi   + 0.15 \bigl( \cos(0.5 \pi \xi) \cos(2 \pi y) \cos(0.5 \pi \zeta) \bigr),
  \\
  z &= \zeta + 0.15 \bigl( \cos(0.5 \pi x) \cos(\pi y) \cos(0.5 \pi \zeta) \bigr).
\end{aligned}
\end{equation}
To integrate up to the
final time $T=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.

>>>>

Currently, \trixi provides shared-memory parallelization via multithreading.
Distributed-memory parallelization with MPI is available for some mesh types;
increasing the capability of this feature is subject to ongoing work.

@@

For the problem setup we consider a periodic box of the domain $[-1,1]^3$ with four elements in each
spatial direction. This results in $64 (\text{\lstinline{polydeg}}+1)^3$ degrees
of freedom (DG nodes) per equation when polynomials of degree \lstinline{polydeg} are used.
To make the mesh curvilinear, the interior of the box is heavily warped by
a mapping adapted from \cite{chan2019efficient}.
Specifically, we map Cartesian reference coordinates $(\xi, \eta, \zeta)$ to
physical coordinates $(x, y, z)$ via the transformation
\begin{equation}
\begin{aligned}
  y &= \eta  + 0.15 \bigl( \cos(1.5 \pi \xi) \cos(0.5 \pi \eta) \cos(0.5 \pi \zeta) \bigr),
  \\
  x &= \xi   + 0.15 \bigl( \cos(0.5 \pi \xi) \cos(2 \pi y) \cos(0.5 \pi \zeta) \bigr),
  \\
  z &= \zeta + 0.15 \bigl( \cos(0.5 \pi x) \cos(\pi y) \cos(0.5 \pi \zeta) \bigr).
\end{aligned}
\end{equation}
To integrate up to the
final time $T=1.0$, both codes use the five-stage, fourth-order low-storage explicit
Runge-Kutta method of Carpenter and Kennedy~\cite{CarpenterKennedy1994}.
A stable explicit time step is adaptively computed according to the local maximum wave
speed, the relative grid size, and an adjustable Courant-Friedrichs-Lewy (CFL)
coefficient $\text{CFL}\in(0,1]$~\cite{gassner2011}. For the performance computations presented herein
we fix this coefficient to be $\text{CFL}=0.5$.
